Crowdy: Social Crowd Visualization

### 2011-04-26 docs/crowdy_gui.tex
Updated Pratheek's part and my part in the documentation.

In the other study based on the previous one, Kamath et al
\cite{krishna:2011}, they add another salient feature - a novel crowd tracking
and evolution approach for linking crowds across time periods. Unlike the more
static and long-lived group-based membership offered on many social networks
their goal was to support the discovery of organic and highly-temporal group
affiliation, which they refer to as ``transient crowds''. A transient crowd
according to them is a potentially short-lived ad-hoc collection of users bound
together by some common thread – which can be communication-based,
location-based or interest based. We are inspired by this idea of formation and
detection of crowds. We try to implement detection of crowd in Crowdy in a
similar fashion.

>>>>

In the other study based on the previous one, Kamath et al
\cite{krishna:2011}, they add another salient feature - a novel crowd tracking
and evolution approach for linking crowds across time periods. Unlike the more
static and long-lived group-based membership offered on many social networks
their goal was to support the discovery of organic and highly-temporal group
affiliation, which they refer to as ``transient crowds''. A transient crowd
according to them is a potentially short-lived ad-hoc collection of users bound
together by some common thread - which can be communication-based,
location-based or interest based. We are inspired by this idea of formation and
detection of crowds. We try to implement detection of crowd in Crowdy in a
similar fashion.

Some other studies related come from areas like social network visualization,
short text visualization, progressive disclosure, and user modeling. Considering
social network visualization , studies like \cite{Boyd:2008} by Boyd et al described features
of on-line social networking sites and the history of the social networking sites,
and the changes during their developments.Deeper understanding of the social
networks can help boost the research in social network visualization. In Moreno's
following work \cite{Moreno:1953}, he emphasized the use of pictorial representations to map
social relations and the embedded patterns. He considered people as nodes in the
network and relations between people as the edges in the network.Laumann et al
\cite{Laumann:1966} applied computational procedure, multidimensional scaling to locate nodes in
visualizing network. The authors are also the first to plot the networks in three
dimensions. Other examples of good visualizations can be Facebook Friend Wheel
\cite{facebook_wheel} which visualizes a Facebook user's network of friends in a wheel format and
Trendsmap \cite{trends_map} which plots real time trending topics over two-dimensional (latitude,
longitude) world map, and you can zoom in to see the trending topics for a specific
location or an area.

In the area of short text visualization, studies like \cite{Bishop:2007} tell that these social
web-sites serve to fulfill their users' desires to interact with and help others.
The authors also proposed a 3-level framework for understanding why members of online
communities participate or not. According to the 3-level framework, users make
comments or short-text post to have their voice be heard. Leggett and Shipman \cite{Leggett:04} 
proposed and described the characteristic of interactive communication in seven
dimensions in a similar way to examine characteristics of communication for a
commenting system like roles,voices,interaction,indirection,history,narrative
and media. In \cite{Hsu:09}, they tried to understand how an on-line community itself
perceives the relative quality of its own user-contributed content and further
used the information to promote valuable opinion from the flood of comments
that attached to each social object.We compared three different visualization
approaches including the traditional list view, the quantitative aggregation
view and the personalized space view. We learned that, to best present massive
metadata such as user contributed comments to the end user, a personalized
filtering model is needed and that a 2D space positional layout is desired
such as in the case of Plurk and Opinion Space systems.

In the area of progressive disclosure, Phan et al built a prototype of a system
that visualized packet traces from a computer network \cite{Phan:07} which is similar to
the problem investigated. They introduced the concept of progressive multiples
which combines progressive disclosure with small multiples. In Scalability in
System Management GUIs \cite{Dieberger:06}, the authors use semantic zooming to show information
about network configuration at various levels of detail, which can tell about
the way progressive disclosure can be used for system administrators.In An
Interactive Ambient Visualization for Code Smells \cite{Murphy:10}, the authors describe a
method for alerting uses about code that may need refactoring. They created a
plug-in for Eclipse that detected questionable code and alerts the programmer.
This shows progressive disclosure for software developers.

Involving user models and visualization into the picture, studies like \cite{Schlungbaum:97} tell
that the individualization often depends on the user's expectation of the user
interface which might be adapted or adaptable or adaptive user interface. Papers
like \cite{Ho:01} explain that the user model selection is crucial for any tool and how
the visualization can help in the discovering and building knowledge. Data and
knowledge visualization module of such a system can be used to help the user
interaction in other modules. This helps in better user interaction experience
irrespective of which module of the system he/she is interacting with.The user's
knowledge, preferences, goals etc. are generally included in the user model when
visualization is concerned in such tools \cite{Henderson}. Also, critical factors like cognitive
load on the user ought to be considered when such tools are made to ensure
effectiveness.The identification of target users is also a important factor to be
considered.Model-based tools like TADEUS can include explicit task and user models
in their system, over potential to work in integrated user interface development
environments and support the entire user interface life cycle. Although research
papers like \cite{Schlungbaum:97}, talk about how different software tools can be used for helping
the user designers create interfaces with consideration of user models , there have
been efforts to combine user model with task and domain models to help developers
in creating and designing user interface \cite{Tran:10}. Systems like DB-USE along with TADEUS
help us in understanding of how user model can be combined with other models to help
in creating/designing better user interface for applications which are mainly
concerned with visualization.
